Contextuality and the Born rule in fuzzy quantum theories

### 2017-03-30 prop_letter.tex
prop_letter.tex Updating...

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Even if quantum mechanics is invented for more than 60 years, mysterious
quantum measurement is still a source of different interpretations
and non-classical phenomena, including non-locality and contextuality~\cite{BellBook1987,Redhead1987-REDINA,peres1995quantum,Jaeger2007}.
In contrast to the idealized measurement process, an actual experiment
is bounded by resources and must be finite precision. Whether finite
precision measurement in reality affect the idealized quantum concept,
e.g., contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
and the very foundation of quantum mechanics is still a problem. In
this letter, we model the finite precision quantum measurement by
quantum interval-valued probability measures (IVPMs) which provides
not only a uniform framework to understand Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
and the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
but also some examples which cannot be explained by the Born rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.

Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly}. In reality, an actual experiment is bounded
by space, time, energy, and other resources so that real measurements
must be finite precision. The tension between finite precision measurement
and the foundation of quantum mechanics sharpened when Meyer~\cite{PhysRevLett.83.3751}
and Kent~\cite{Kent1999} proved the original definition of contextuality
based on infinitely precised complex numbers cannot be experimental
verified. There were a long debate about whether contextuality could
be experimental verified or not~\cite{Mermin1999,Peres2003,BarrettKent2004}.
After the debates, people are still trying to update the definition
of contextuality when they want to perform further experiment~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

In order to analyze the quantum world with finite resource, we extend
the classical interval-valued probability measure (IVPM)~\cite{JamisonLodwick2004},
and introduce a new framework: quantum IVPM...\newpage{}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Textbook quantum mechanics asserts that the probability of a measurement
can be computed from wave function of the system and the measuring
observable \emph{exactly} while real measurements must be finite precision.
Whether finite precision measurement in reality affect the idealized
quantum concept, e.g., contextuality~\cite{PhysRevLett.83.3751,Mermin1999,BarrettKent2004},
and the very foundation of quantum mechanics is still a problem. In
this letter, we model the finite precision quantum measurement by
quantum interval-valued probability measures (IVPMs) which provides
not only a uniform framework to understand Gleason's theorem~\cite{gleason1957,Redhead1987-REDINA,peres1995quantum}
and the Kochen-Specker theorem~\cite{kochenspecker1967,peres1995quantum,Redhead1987-REDINA}
but also some examples which cannot be explained by the Born rule~\cite{Born1983,peres1995quantum,544199,Jaeger2007}.

The tension between finite precision measurement and the foundation
of quantum mechanics sharpened when the original definition of contextuality
based on infinitely precised numbers is proved not experimental verifiable~\cite{PhysRevLett.83.3751,Kent1999}.
After a long debate~\cite{Mermin1999,Peres2003,BarrettKent2004},
people are still trying to update the definition of contextuality
when they want to perform further experiments~\cite{Spekkens2005,GuehneKleinmannCabelloEtAl2010,MazurekPuseyKunjwalEtAl2016}.

We found that finite precision measurement affects not only contextuality
but also the fundamental rule computing probability from a state.
In the early formulation of quantum mechanics, von Neumann essentially
formulated a quantum state as a density matrix while Mackey formulated
a quantum state as a probability measure which are proved to be the
same as a density matrix by Gleason's theorem~\cite{Varadarajan2008}.
If we follow Mackey's idea of probability measures together with the
classical IVPM~\cite{JamisonLodwick2004} which could be used to
formulate finite precision measurement in classical situation, we
can define quantum IVPMs. Surprisingly, there is a quantum IVPM which
can not be induced by a density matrix according to the Born rule.
Similar to the tension between finite precision and contextuality
are still inspiring experimental testable definition of contextuality,
the very basic definition of a quantum state or how to compute the
probability from a state might need to be refined when we consider
the finite precision measurement. \newpage{}
